---
title: "ggradar"
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 300, message = FALSE, warning = FALSE, error = FALSE)
```

`ggradar` allows you to build radar charts with ggplot2. This package is based on [Paul Williamson's](http://rstudio-pubs-static.s3.amazonaws.com/5795_e6e6411731bb4f1b9cc7eb49499c2082.html) code, with new aesthetics and compatibility with ggplot2 2.0.

It was inspired by [d3radaR](http://www.buildingwidgets.com/blog/2015/12/9/week-49-d3radarr), an htmlwidget built by [timelyportfolio](https://github.com/timelyportfolio).

## Install `ggradar`

```{r, eval=FALSE}
devtools::install_github("ricardo-bion/ggradar", 
                          dependencies = TRUE)
```

## Use `ggradar`

```{r, fig.width=15, fig.height=10}
library(ggradar)
library(dplyr)
library(scales)
library(tibble)

mtcars_radar <- mtcars %>% 
  as_tibble(rownames = "group") %>% 
  mutate_at(vars(-group), rescale) %>% 
  tail(4) %>% 
  select(1:10)
```

```{r, echo = FALSE}
knitr::kable(mtcars_radar,format = "markdown") 
```

```{r}
ggradar(mtcars_radar)
```

## Custom fonts

You can also use custom font family in `ggradar`. In the following example, you would like to use Airbnb's font family named 'Circular Air' by first downloading it, installing it in your computer (not shown), and then registering it to R using `extrafont` package.

```{r, eval = FALSE}
# configured to work on a Mac, change directory to Unix or Windows
download.file("https://github.com/ricardo-bion/ggtech/blob/master/Circular%20Air-Light%203.46.45%20PM.ttf", "~/Circular Air-Light 3.46.45 PM.ttf", method = "curl")

extrafont::font_import(pattern = 'Circular', prompt = FALSE)
```

Following the same procedure as in the previous example, you can then use 'Circular Air' font family in `ggradar` by adjusting `font.radar` argument. The following example shows that `ggradar` is also can be used in pipe `%>%`.

```{r, fig.width=15, fig.height=10}
mtcars %>% 
  as_tibble(rownames = "group") %>% 
  mutate_at(vars(-group), rescale) %>% 
  tail(4) %>% 
  select(1:10) %>% 
  ggradar(font.radar = "Circular Air")
```

